Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-04 report/report.tex
Split up Intructions in subsections
TOC depth 1
Update todo
Organize delimitations and implementation overview into Methodology
Organize background section

\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\setcounter{tocdepth}{2}

@@

@@

Cities consist of complex collections of buildings, blocks, parcels and neighbourhoods which are all interconnected via a street network, where individual streets can serve different types of traffic.
These features are commonly represented as geodata in map databases, and processed and organized into visualization-ready data by a Geographic Information System (GIS).
In practise, cities are often made up out of many square kilometers worth of geodata, and it would be highly labour intensive to recreate all the features in 3D.
Instead, procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak through interfaces fo interactive editing.
At the very base of this process is the procedural layout of road networks in 3D,
\textbf{(Müller et al, 2006)}
and so far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities, particularily due to the interest in self-propelled cars.
The study of energy efficient mobility such as walking and cycling is only in its emerging phase. \textbf{(Stojanovski, 2019)}

@@

@@

\section{Methodology}

@@

This section will dive into the state-of-the-art use of city reconstruction methods within the research field of urban design.
The first section will present the motivations for the digitization of urban planning, as well as the most common programs and tools in this area, which are after all not very commonly used in the practise of urban design due to the failure in being able to reflect the unique workspace of urban designers.
The Related work section will present a brief history of the field of OpenStreetMap data qualification, and present the research papers whose methods are at the foundation of this project.

\section{Background of 3D city reproduction}

@@

\section{Related work}
When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers.
\textbf{(Van Oort, 2006)} Since then a number of publications have examined slices of geodata from van Oort's criteria.
In 2008, \textbf{(Haklay, 2010)} conducted such a study to estimate of the quality of OSM positional geodata in London and England.
Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset.
The study was conducted by comparing OSM data to Ordnance Survey datasets.
The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset.
However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

@@

\subsection{Other accuracy criteria}

@@

@@

% Torsdag:
% TODO: Mention that positional accuracy will be the focus early on
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Split up introduction, more subsections
% TODO: Delimitations in Introduction, after RQ
% TODO: Move: 2.1.1: Accuracy criteria that will not be focused on -> Delimitations

>>>>

\setlength\parindent{0pt}
\setlength{\parskip}{1em}
\setcounter{tocdepth}{1}

@@

\section{Introduction to virtual cities}

@@

@@

\section{Accuracy limitations in 3D city reproduction}

@@

@@

This section will dive into the state-of-the-art use of city reconstruction methods within the research field of urban design.
This chapter will present the motivations for the digitization of urban planning, as well as the most common programs and tools in this area, which are after all not very commonly used in the practise of urban design due to the failure in being able to reflect the unique workspace of urban designers.
The final section will present a brief history of the field of OpenStreetMap data qualification, and present the research papers whose methods are at the foundation of this project.

\section{Overview of virtual cities}

Cities consist of complex collections of \textbf{buildings}, \textbf{blocks}, \textbf{parcels} and \textbf{neighbourhoods} which are all interconnected via a \textbf{street} network, where individual streets can serve different types of traffic.
These features are commonly represented as \textbf{geodata} in map databases, and processed and organized into visualization-ready data by a \textbf{Geographic Information System (GIS)}.
In practise, cities are often made up out of many square kilometers worth of geodata, and it would be highly labour intensive to recreate all the features in 3D.
Instead, \textbf{procedural models} for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak through interfaces fo interactive editing.
At the very base of this process is the procedural layout of road networks in 3D,
\textbf{(Müller et al, 2006)}
and so far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities, particularily due to the interest in self-propelled cars.
The study of energy efficient mobility such as walking and cycling is only in its emerging phase. \textbf{(Stojanovski, 2019)}

\section{3D city reproduction as a research field}

@@

\section{Previous work in qualifying OpenStreetMap data}

When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers.
\textbf{(Van Oort, 2006)} Since then a number of publications have examined slices of geodata from van Oort's criteria.
In 2008, \textbf{(Haklay, 2010)} conducted such a study to estimate of the quality of OSM positional geodata in London and England.
Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset.
The study was conducted by comparing OSM data to Ordnance Survey datasets.
The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset.
However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

@@

@@

\section{Implementation overview}

@@

% Torsdag:
% TODO: Move content from chapters 1, 3 and 4 to Background
% TODO: Mention that positional accuracy will be the focus early on
